---
format: gfm
---

# BPos

This R package provides functions for simulating repeated opponent processes using the behavioral posology paradigm and for using Bode plots to analyze the healthy hormetic limits of behaviors.

## Installation

You can install the bpos package by running the following code in R or RStudio:

```{r}

# install.packages("bpos")
## REPLACE WITH GITHUB NAME

```

## Usage
### Simulating Opponent Processes

You can create Bode plots using the bode_plot() function as follows:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot()

```

You can also plot the graphs individually:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(join_plots=FALSE)

```

You can test how varying parameters in the utility function affects the opponent processes, and in turn affects the hormetic curve. For example, you can increase the b-process curvature:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

```

.....................................

For more usage examples and detailed explanations, please refer to the package documentation by using the 'help()' function in R. 

## License

This package is released under the MIT License.





<!-- # Testing out JUST PK alterations. Can STILL ACHIEVE HORMESIS?? -->

<!-- ```{r} -->
<!-- #| fig-width: 9 -->
<!-- #| fig-height: 12 -->
<!-- #| warning: false -->
<!-- #| results: 'hide' -->
<!-- #| fig-dpi: 600 -->

<!-- bode_plot(EC50_b = c(0.8, 0.9, 1, 1.1), k_bpk = 0.02, seq_2 = 0.08, plot_2 = c(0.0015, 0.08)) -->

<!-- ``` -->

<!-- # Work on a combined figure leading up to final hormetic eigenvector -->

<!-- ```{r} -->
<!-- #| fig-width: 9 -->
<!-- #| fig-height: 12 -->
<!-- #| warning: false -->
<!-- #| results: 'hide' -->
<!-- #| fig-dpi: 300 -->

<!-- bode_plot(EC50_b=c(2.1, 2.8, 3.5, 4.2), seq_1=0.00025, sim_length=4000, gg_ylim=-500, meta_curve=TRUE) -->

<!-- ``` -->

<!-- # Repeat, but show that modifying a-process does little to shift hormetic curve -->

<!-- ```{r} -->
<!-- #| fig-width: 9 -->
<!-- #| fig-height: 12 -->
<!-- #| warning: false -->
<!-- #| results: 'hide' -->
<!-- #| fig-dpi: 300 -->

<!-- bode_plot(EC50_a=c(0.6, 0.8, 1.1, 1.5), seq_1=0.00025, sim_length=4000, gg_ylim=-500, meta_curve=TRUE) -->

<!-- ``` -->
