---
format: gfm
---

# BPos

This R package provides functions for simulating repeated opponent processes using the behavioral posology paradigm and for using Bode plots to analyze the healthy hormetic limits of behaviors.

## Installation

You can install the bpos package by running the following code in R or RStudio:

```{r}

# install.packages("bpos")
# library(bpos)
## REPLACE WITH GITHUB NAME

```

## Usage
### Simulating Opponent Processes

You can create Bode plots using the bode_plot() function as follows:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot()

```

You can also plot the graphs individually:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(join_plots=FALSE)

```

You can test how varying parameters in the utility function affects the opponent processes, and in turn affects the hormetic curve. For example, you can increase the b-process curvature in the utility function:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(gamma_b=c(0.7, 0.9, 1.1))

```

Or increase the magnitude of the loss side of the utility function:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(lambda_b=c(2, 2.5, 3))

```

You can also modify the a-process curvature in the utility function:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(gamma_a=c(0.5, 0.7, 0.9), colorscheme=2)

```

Or increase the magnitude of the gain side of the utility function:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(lambda_b=c(1, 1.5, 2), colorscheme=2)

```

You can modify the pharmacodynamic decay constant for the a-process:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(k_apd=c(0.5, 1, 1.5), colorscheme=3)

```

Or modify the pharmacodynamic decay constant for the b-process:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(k_bpd=c(1.5, 2, 2.5), colorscheme=3)

```

Likewise, you can modify the pharmacokinetic decay constant for the a-process:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(k_apk=c(0.01, 0.02, 0.03), colorscheme=4)

```

Or modify the pharmacokinetic decay constant for the b-process:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(k_bpk=c(0.01, 0.02, 0.03), colorscheme=4)

```

You can also extend the Bode plot:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300



```

You can also cut off behaviors at a certain point, so that they stay within the hormetic limit:

```{r}
#| fig-width: 9
#| fig-height: 12
#| warning: false
#| results: 'hide'
#| fig-dpi: 300

bode_plot(addl = 40)

```

For more usage examples and detailed explanations, please refer to the package documentation by using the 'help()' function in R. 

## License

This package is released under the MIT License.